### 2021-09-09 paper/output/document/paper31.tex
added outline, began Kroy tests

\isamarkupcmt{Nitpick tells us that the FUL is consistent%

@@

One category of tests is specified models. Specifying the model allows us to encode certain facts 

@@

\ lying{\isacharunderscore}not{\isacharunderscore}universal{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}bool{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}lying{\isacharunderscore}not{\isacharunderscore}universal\ {\isasymequiv}\ {\isasymnot}\ {\isacharparenleft}{\isasymforall}x{\isachardot}\ lie{\isacharparenleft}x{\isacharparenright}\ cw{\isacharparenright}\ {\isasymand}\ {\isacharparenleft}lie{\isacharparenleft}me{\isacharparenright}\ cw{\isacharparenright}{\isachardoublequoteclose}%

@@

This is a rough translation of failure of the universalizability test: we will the maxim universally,

@@

  Free variable:
    lie = ($\lambda x. \_$)($p_1$ := ($\lambda x. \_$)($i_1$ := True, $i_2$ := False), $p_2$ := ($\lambda x. \_$)($i_1$ := False, $i_2$ := False)) \color{black}%
}\isanewline
%
\isamarkupcmt{Quick note on how to read Nitpick results. Nitpick will either say that it found a ``model" or a ``counterexample" in 
the first line. It will then provide a model by specifying model components. For readability, all except for the 
free variables are hidden. This model has cardinality 2 for the person and world (i) types. The term \texttt{lie} is 
defined for people $p_1$ and $p_2$. $p_1$ lies at world $i_1$ and does not lie at world $i_2$. $p_2$ does
the opposite.%
}\isanewline
%
\isamarkupcmt{These details will be elided for most Nitpick examples, but this provides guidance on how to interpret
the output.%
}%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\begin{isamarkuptext}%
This formula isn't valid. While the FUL should tell us that lying is prohibited, the fact that it 
doesn't demonstrates the weakness of this naive formulation of the categorical imperative. Kant's version of
the FUL universalizes across people, as we did in the definition of \isa{lying{\isacharunderscore}not{\isacharunderscore}universal\ {\isasymequiv}\ {\isasymnot}\ {\isacharparenleft}{\isasymforall}x{\isachardot}\ lie\ x\ cw{\isacharparenright}\ {\isasymand}\ lie\ me\ cw}. The 
naive formalization universalizes across worlds using the $\Box$ operator, so it makes sense that it can't
handle this example appropriately.

@@

%:%74=33%:%
%:%75=34%:%
%:%76=35%:%
%:%77=36%:%
%:%78=37%:%
%:%79=38%:%
%:%80=39%:%
%:%81=40%:%
%:%83=42%:%
%:%84=42%:%
%:%85=43%:%
%:%87=45%:%
%:%88=46%:%
%:%89=47%:%
%:%90=48%:%
%:%91=49%:%
%:%92=50%:%
%:%93=51%:%
%:%94=52%:%
%:%95=53%:%
%:%96=54%:%
%:%97=55%:%
%:%98=56%:%
%:%100=59%:%
%:%101=59%:%
%:%102=59%:%
%:%104=59%:%
%:%108=59%:%
%:%109=59%:%
%:%111=60%:%
%:%112=61%:%
%:%113=62%:%
%:%114=62%:%
%:%116=63%:%
%:%183=110%:%
%:%195=112%:%
%:%196=113%:%
%:%197=114%:%
%:%198=115%:%
%:%200=117%:%
%:%201=117%:%
%:%202=118%:%
%:%203=118%:%
%:%215=126%:%
%:%218=127%:%
%:%219=127%:%
%:%221=128%:%
%:%222=129%:%
%:%223=130%:%
%:%224=131%:%
%:%225=131%:%
%:%226=132%:%
%:%227=133%:%
%:%228=133%:%
%:%229=134%:%
%:%230=135%:%
%:%233=136%:%
%:%237=136%:%
%:%238=136%:%
%:%239=136%:%
%:%241=137%:%
%:%242=138%:%
%:%252=140%:%
%:%253=141%:%
%:%254=142%:%
%:%258=144%:%
%:%260=146%:%
%:%261=146%:%
%:%262=147%:%
%:%263=147%:%
%:%264=148%:%
%:%265=148%:%
%:%267=149%:%
%:%268=149%:%
%:%269=150%:%
%:%270=151%:%
%:%271=151%:%
%:%273=153%:%
%:%274=154%:%
%:%275=155%:%
%:%276=156%:%
%:%278=158%:%
%:%279=158%:%
%:%280=159%:%
%:%281=160%:%
%:%282=161%:%
%:%283=161%:%
%:%286=162%:%
%:%290=162%:%
%:%291=162%:%
%:%293=163%:%
%:%294=164%:%
%:%295=165%:%
%:%296=166%:%
%:%297=166%:%
%:%299=167%:%
%:%300=168%:%
%:%301=169%:%
%:%302=170%:%
%:%303=171%:%
%:%304=171%:%
%:%306=172%:%
%:%307=173%:%
%:%317=175%:%
%:%318=176%:%
%:%319=177%:%
%:%320=178%:%
%:%321=179%:%
%:%322=180%:%
%:%323=181%:%
%:%324=182%:%
%:%326=184%:%
%:%327=184%:%
%:%328=185%:%
%:%329=186%:%
%:%330=187%:%
%:%331=187%:%
%:%333=187%:%
%:%337=187%:%
%:%338=187%:%
%:%340=188%:%
%:%341=189%:%
%:%342=190%:%
%:%343=191%:%
%:%344=192%:%
%:%345=193%:%
%:%355=195%:%
%:%356=196%:%
%:%357=197%:%
%:%358=198%:%
%:%359=199%:%
%:%360=200%:%
%:%369=202%:%
%:%381=204%:%
%:%382=205%:%
%:%383=206%:%
%:%384=207%:%
%:%385=208%:%
%:%386=209%:%
%:%387=210%:%
%:%388=211%:%
%:%389=212%:%
%:%390=213%:%
%:%391=214%:%
%:%392=215%:%
%:%394=217%:%
%:%395=217%:%
%:%396=218%:%
%:%397=219%:%
%:%398=220%:%
%:%399=220%:%
%:%401=220%:%
%:%405=220%:%
%:%406=220%:%
%:%408=221%:%
%:%409=222%:%
%:%410=223%:%
%:%411=224%:%
%:%412=224%:%
%:%414=225%:%
%:%415=226%:%
%:%416=226%:%
%:%418=227%:%
%:%419=228%:%
%:%429=230%:%
%:%430=231%:%
%:%432=233%:%
%:%433=233%:%
%:%434=234%:%
%:%435=235%:%
%:%436=236%:%
%:%437=236%:%
%:%439=236%:%
%:%443=236%:%
%:%444=236%:%
%:%446=237%:%
%:%447=238%:%
%:%448=239%:%
%:%449=240%:%
%:%450=240%:%
%:%452=241%:%
%:%462=243%:%
%:%466=245%:%
%:%467=246%:%
%:%468=247%:%
%:%469=248%:%
%:%471=250%:%
%:%472=250%:%
%:%473=251%:%
%:%474=252%:%
%:%475=253%:%
%:%476=253%:%
%:%478=253%:%
%:%482=253%:%
%:%483=253%:%
%:%485=254%:%
%:%486=255%:%
%:%487=256%:%
%:%488=257%:%
%:%489=257%:%
%:%491=258%:%
%:%501=260%:%
%:%502=261%:%
%:%503=262%:%
%:%505=264%:%
%:%506=264%:%
%:%507=265%:%
%:%508=266%:%
%:%509=267%:%
%:%510=267%:%
%:%512=267%:%
%:%516=267%:%
%:%517=267%:%
%:%519=268%:%
%:%520=269%:%
%:%521=270%:%
%:%522=270%:%
%:%524=271%:%
%:%534=273%:%
%:%535=274%:%
%:%536=275%:%
%:%538=277%:%
%:%539=277%:%
%:%540=278%:%
%:%541=279%:%
%:%542=280%:%
%:%543=281%:%
%:%544=282%:%
%:%545=282%:%
%:%552=283%:%
%:%553=283%:%
%:%554=284%:%
%:%555=284%:%
%:%556=285%:%
%:%557=285%:%
%:%558=286%:%
%:%559=286%:%
%:%560=286%:%
%:%561=286%:%
%:%563=287%:%
%:%564=288%:%
%:%565=288%:%
%:%566=289%:%
%:%567=289%:%
%:%568=289%:%
%:%570=290%:%
%:%571=291%:%
%:%572=292%:%
%:%573=293%:%
%:%574=294%:%
%:%575=294%:%
%:%577=295%:%
%:%587=297%:%
%:%588=298%:%
%:%589=299%:%
%:%590=300%:%
%:%591=301%:%
%:%593=303%:%
%:%594=303%:%
%:%595=304%:%
%:%596=305%:%
%:%597=306%:%
%:%598=306%:%
%:%600=306%:%
%:%604=306%:%
%:%605=306%:%
%:%607=307%:%
%:%608=308%:%
%:%609=309%:%
%:%610=310%:%
%:%611=311%:%
%:%621=313%:%
%:%622=314%:%
%:%626=316%:%
%:%630=318%:%
%:%631=319%:%
%:%632=320%:%
%:%634=322%:%
%:%635=322%:%
%:%636=323%:%
%:%639=324%:%
%:%643=324%:%
%:%644=324%:%
%:%646=325%:%
%:%647=325%:%
%:%649=326%:%
%:%650=327%:%
%:%651=328%:%
%:%652=329%:%
%:%653=330%:%
%:%663=332%:%
%:%664=333%:%
%:%665=334%:%
%:%666=335%:%
%:%668=337%:%
%:%669=337%:%
%:%670=338%:%
%:%673=339%:%
%:%677=339%:%
%:%678=339%:%
%:%679=339%:%
%:%681=340%:%
%:%682=340%:%

>>>>

\isamarkupcmt{Nitpick tells us that the FUL is consistent\footnote{``oops" at the end of a lemma indicates that the 
proof is left unfinished. It does not indicate that an error occurred. In this case, we aren't interested
in proving True (the proof is trivial and automatic), hence the oops.}%

@@

One category of tests involves specified models to encode certain facts 

@@

\ lying{\isacharunderscore}not{\isacharunderscore}universal{\isacharcolon}{\isacharcolon}{\isachardoublequoteopen}bool{\isachardoublequoteclose}\ \isakeyword{where}\ {\isachardoublequoteopen}lying{\isacharunderscore}not{\isacharunderscore}universal\ {\isasymequiv}\ {\isasymforall}w{\isachardot}\ {\isasymnot}\ {\isacharparenleft}{\isacharparenleft}{\isasymforall}x{\isachardot}\ lie{\isacharparenleft}x{\isacharparenright}\ w{\isacharparenright}\ {\isasymand}\ {\isacharparenleft}lie{\isacharparenleft}me{\isacharparenright}\ w{\isacharparenright}{\isacharparenright}{\isachardoublequoteclose}%

@@

This is a rough translation of failure of the universalizability test: we will test the maxim universally,

@@

  Free variable:
    lie = ($\lambda x. \_$)($p_1$ := ($\lambda x. \_$)($i_1$ := True, $i_2$ := False), $p_2$ := ($\lambda x. \_$)($i_1$ := False, $i_2$ := False)) \color{black}%
}\isanewline
%
\isamarkupcmt{Quick note on how to read Nitpick results. Nitpick will either say that it found a ``model" or a ``counterexample" in 
the first line. It will then provide a model by specifying model components. For readability, all except for the 
free variables are hidden. This model has cardinality 2 for the person and world (i) types. The term \texttt{lie} is 
defined for people $p_1$ and $p_2$. $p_1$ lies at world $i_1$ and does not lie at world $i_2$. $p_2$ does
the opposite.%
}\isanewline
%
\isamarkupcmt{These details will be elided for most Nitpick examples, but this provides guidance on how to interpret
the output.%
}%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\begin{isamarkuptext}%
This formula isn't valid. While the FUL should tell us that lying is prohibited, the fact that it 
doesn't demonstrates the weakness of this naive formulation of the categorical imperative. Kant's version of
the FUL universalizes across people, as we did in the definition of \isa{lying{\isacharunderscore}not{\isacharunderscore}universal\ {\isasymequiv}\ {\isasymforall}w{\isachardot}\ {\isasymnot}\ {\isacharparenleft}{\isacharparenleft}{\isasymforall}x{\isachardot}\ lie\ x\ w{\isacharparenright}\ {\isasymand}\ lie\ me\ w{\isacharparenright}}. The 
naive formalization universalizes across worlds using the $\Box$ operator, so it makes sense that it can't
handle this example appropriately.

@@

%:%74=27%:%
%:%75=28%:%
%:%76=29%:%
%:%77=30%:%
%:%78=31%:%
%:%79=32%:%
%:%80=33%:%
%:%81=34%:%
%:%83=36%:%
%:%84=36%:%
%:%85=37%:%
%:%87=39%:%
%:%88=40%:%
%:%89=41%:%
%:%90=42%:%
%:%91=43%:%
%:%92=44%:%
%:%93=45%:%
%:%94=46%:%
%:%95=47%:%
%:%96=48%:%
%:%97=49%:%
%:%98=50%:%
%:%100=53%:%
%:%101=53%:%
%:%102=53%:%
%:%104=53%:%
%:%108=53%:%
%:%109=53%:%
%:%111=54%:%
%:%112=55%:%
%:%113=56%:%
%:%114=56%:%
%:%116=57%:%
%:%117=58%:%
%:%118=59%:%
%:%119=59%:%
%:%186=105%:%
%:%198=107%:%
%:%199=108%:%
%:%200=109%:%
%:%201=110%:%
%:%203=112%:%
%:%204=112%:%
%:%205=113%:%
%:%206=113%:%
%:%218=121%:%
%:%221=122%:%
%:%222=122%:%
%:%224=123%:%
%:%225=124%:%
%:%226=125%:%
%:%227=126%:%
%:%228=126%:%
%:%229=127%:%
%:%230=128%:%
%:%231=128%:%
%:%232=129%:%
%:%233=130%:%
%:%236=131%:%
%:%240=131%:%
%:%241=131%:%
%:%242=131%:%
%:%244=132%:%
%:%245=133%:%
%:%255=135%:%
%:%256=136%:%
%:%257=137%:%
%:%261=139%:%
%:%263=141%:%
%:%264=141%:%
%:%265=142%:%
%:%266=142%:%
%:%267=143%:%
%:%268=143%:%
%:%270=144%:%
%:%271=144%:%
%:%272=145%:%
%:%273=146%:%
%:%274=146%:%
%:%276=148%:%
%:%277=149%:%
%:%278=150%:%
%:%279=151%:%
%:%281=153%:%
%:%282=153%:%
%:%283=154%:%
%:%284=155%:%
%:%285=156%:%
%:%286=156%:%
%:%289=157%:%
%:%293=157%:%
%:%294=157%:%
%:%296=158%:%
%:%297=159%:%
%:%298=160%:%
%:%299=161%:%
%:%300=161%:%
%:%302=162%:%
%:%303=163%:%
%:%304=164%:%
%:%305=165%:%
%:%306=166%:%
%:%307=166%:%
%:%309=167%:%
%:%310=168%:%
%:%320=170%:%
%:%321=171%:%
%:%322=172%:%
%:%323=173%:%
%:%324=174%:%
%:%325=175%:%
%:%326=176%:%
%:%327=177%:%
%:%329=179%:%
%:%330=179%:%
%:%331=180%:%
%:%332=181%:%
%:%333=182%:%
%:%334=182%:%
%:%336=182%:%
%:%340=182%:%
%:%341=182%:%
%:%343=183%:%
%:%344=184%:%
%:%345=185%:%
%:%346=186%:%
%:%347=187%:%
%:%348=188%:%
%:%358=190%:%
%:%359=191%:%
%:%360=192%:%
%:%361=193%:%
%:%362=194%:%
%:%363=195%:%
%:%372=197%:%
%:%384=199%:%
%:%385=200%:%
%:%386=201%:%
%:%387=202%:%
%:%388=203%:%
%:%389=204%:%
%:%390=205%:%
%:%391=206%:%
%:%392=207%:%
%:%393=208%:%
%:%394=209%:%
%:%395=210%:%
%:%397=212%:%
%:%398=212%:%
%:%399=213%:%
%:%400=214%:%
%:%401=215%:%
%:%402=215%:%
%:%404=215%:%
%:%408=215%:%
%:%409=215%:%
%:%411=216%:%
%:%412=217%:%
%:%413=218%:%
%:%414=219%:%
%:%415=219%:%
%:%417=220%:%
%:%418=221%:%
%:%419=221%:%
%:%421=222%:%
%:%422=223%:%
%:%432=225%:%
%:%433=226%:%
%:%435=228%:%
%:%436=228%:%
%:%437=229%:%
%:%438=230%:%
%:%439=231%:%
%:%440=231%:%
%:%442=231%:%
%:%446=231%:%
%:%447=231%:%
%:%449=232%:%
%:%450=233%:%
%:%451=234%:%
%:%452=235%:%
%:%453=235%:%
%:%455=236%:%
%:%465=238%:%
%:%469=240%:%
%:%470=241%:%
%:%471=242%:%
%:%472=243%:%
%:%474=245%:%
%:%475=245%:%
%:%476=246%:%
%:%477=247%:%
%:%478=248%:%
%:%479=248%:%
%:%481=248%:%
%:%485=248%:%
%:%486=248%:%
%:%488=249%:%
%:%489=250%:%
%:%490=251%:%
%:%491=252%:%
%:%492=252%:%
%:%494=253%:%
%:%504=255%:%
%:%505=256%:%
%:%506=257%:%
%:%508=259%:%
%:%509=259%:%
%:%510=260%:%
%:%511=261%:%
%:%512=262%:%
%:%513=262%:%
%:%515=262%:%
%:%519=262%:%
%:%520=262%:%
%:%522=263%:%
%:%523=264%:%
%:%524=265%:%
%:%525=265%:%
%:%527=266%:%
%:%537=268%:%
%:%538=269%:%
%:%539=270%:%
%:%541=272%:%
%:%542=272%:%
%:%543=273%:%
%:%544=274%:%
%:%545=275%:%
%:%546=276%:%
%:%547=277%:%
%:%548=277%:%
%:%555=278%:%
%:%556=278%:%
%:%557=279%:%
%:%558=279%:%
%:%559=280%:%
%:%560=280%:%
%:%561=281%:%
%:%562=281%:%
%:%563=281%:%
%:%564=281%:%
%:%566=282%:%
%:%567=283%:%
%:%568=283%:%
%:%569=284%:%
%:%570=284%:%
%:%571=284%:%
%:%573=285%:%
%:%574=286%:%
%:%575=287%:%
%:%576=288%:%
%:%577=289%:%
%:%578=289%:%
%:%580=290%:%
%:%590=292%:%
%:%591=293%:%
%:%592=294%:%
%:%593=295%:%
%:%594=296%:%
%:%596=298%:%
%:%597=298%:%
%:%598=299%:%
%:%599=300%:%
%:%600=301%:%
%:%601=301%:%
%:%603=301%:%
%:%607=301%:%
%:%608=301%:%
%:%610=302%:%
%:%611=303%:%
%:%612=304%:%
%:%613=305%:%
%:%614=306%:%
%:%624=308%:%
%:%625=309%:%
%:%629=311%:%
%:%633=313%:%
%:%634=314%:%
%:%635=315%:%
%:%637=317%:%
%:%638=317%:%
%:%639=318%:%
%:%642=319%:%
%:%646=319%:%
%:%647=319%:%
%:%649=320%:%
%:%650=320%:%
%:%652=321%:%
%:%653=322%:%
%:%654=323%:%
%:%655=324%:%
%:%656=325%:%
%:%666=327%:%
%:%667=328%:%
%:%668=329%:%
%:%669=330%:%
%:%671=332%:%
%:%672=332%:%
%:%673=333%:%
%:%676=334%:%
%:%680=334%:%
%:%681=334%:%
%:%682=334%:%
%:%684=335%:%
%:%685=335%:%
